### 2015-07-05 narrative/naming-service.tex
fixed the research questions

Given the well documented difficulties with POSIX-compliant naming and our
approach that decomposes what would be a single file into potentially large
number of objects, we must take a new approach to naming.  Data migration, as a
result of system pressures or user/system policies, further adds to the
complexity of managing naming and discovery. Our naming service must maintain
sufficient metadata information, track or be able to find objects as they move
across storage layers, and facilitates data discovery.

@@

The overriding theme for this proposal of providing a cooperative relationship
between the user and the storage system extends into this area as well.
Negotiating the data quality/retrieval time tradeoff reuqires additional data.
Providing this functionality requries the naming service be able to both return
a list of data versions and an indication of data quality. This will be
combined with a retrieval time estimate for each verstion by the middleware to
determine what data version should be retrieved.  This estimate will be
disucssed elsewhere in this proposal.

Structurally, the traditional POSIX naming service offeriing a hierarchical
space consisting of directories and files may be maintained for backwards
compatibility. However, this view will not offer the same strict semantics
POSIX defines. We must break these strict semantics to address scalability
problems forced by the serialized access to a single source for creating and
accessing files.  Several efforts~\cite{giga+,pvfs,others} have worked to
reduce this contention by doing things like reducing the serialized scope to a
single directory or subtree. While these approaches help, they do not address
this key scalability limitation of serialized access--even if the metadata
service is spread across multiple nodes. Instead, we will offer a
short duration to consistency POSIX view to offer the performance and
consistency requirements an exascale application demands.

>>>>

Given the well documented difficulties with POSIX-compliant naming and our
approach that decomposes what would be a single file into potentially large
number of objects, we must take a new approach to naming.  Data migration, as a
result of system pressures or user/system policies, further adds to the
complexity of managing naming and discovery. Our naming service must maintain
sufficient metadata information, track or be able to find objects as they move
across storage layers, and facilitates data discovery. Since we need to also
support access through POSIX APIs for existing application and system
integration, we must address how to bridge the drastic differences between the
decomposed objects of potentially varying fidelity with potentially multiple
version with a POSIX API-compatible interface.

Our research in this area will address the following questions:\\
Since our metadata is distributed and partitioned, how do we respond to user
  requests within a specified time bound with accuracy? How do we estimate the
  completeness of the response?\\
For POSIX API requests, how do we respond if only varying data fidelity levels
  are available for the requested data object?\\
What level of metadata should we maintain and keep in sync to enhance response
  quality within time-bound requests?\\
How much time should be allowed for searching for metadata given the user
  specified limits for data retrieval since the user will still have to spend
  the data retrieval time from different devices? How do we integrate the read
  time overhead into the metadata requests?\\
How do we provide appropriate security while maintaining scalability,
  particularly with the distributed metadata stores?\\
% Which data block and what quality/type do we respond to a query with?;\\
% How will we scale a fully distributed storage system's metadata management;\\
% Can we accelerate the discovery process with the addition of an
%    application/user level metadata store that tracks where data was
%    originally written and how was it structured?;\\
% Can we provide time estimates for read/write calls in the presence of
%    an unbounded discovery system? If not how do we bound the discovery time?
% How do we amortize the time cost of discovery vs time cost of actually
%    reading the data (latency vs bandwidth essentially)?

@@

The overriding theme for this proposal of providing a cooperative relationship
between the user and the storage system extends into this area as well.
Negotiating the data quality/retrieval time tradeoff reuqires additional
metadata.  Providing this functionality requries the naming service be able to
both return a list of data versions and an indication of data quality. This
will be combined with a retrieval time estimate for each verstion by the
middleware to determine what data version should be retrieved.  This estimate
will be disucssed elsewhere in this proposal.

Structurally, the traditional POSIX naming service offeriing a hierarchical
space consisting of directories and files may be maintained for backwards
compatibility. However, this view will not offer the same strict semantics
POSIX defines. We must break these strict semantics to address scalability
problems forced by the serialized access to a single source for creating and
accessing files.  Several efforts~\cite{giga+,pvfs,others} have worked to
reduce this contention by doing things like reducing the serialized scope to a
single directory or subtree or allowing a single process in a collective file
operation talk with the metadata service and distribute a handle to other
participants. While these approaches help, they do not address this key
scalability limitation of serialized access--even if the metadata service is
spread across multiple nodes. Instead, we will offer a short duration to
consistency POSIX view to offer the performance and consistency requirements an
exascale application demands.
